---
title: "MetabCombiner Multibatch Alignment Report"
output: html_document
params:
  project_name: ""
  input_stats: ""
  filter_plot: ""
  alignment_heatmap: ""
  percent_aligned_plot: ""
  percent_aligned_filtered_plot: ""
  adduct_plot:
  max_missing_in_pools: 30,
  max_missing_in_samples: 50
---

## **`r params$project_name`**.

#### Input data are filtered based on the following parameters:
* Max. % missing in pools: **`r params$max_missing_in_pools`%**
* Max. % missing in samples: **`r params$max_missing_in_samples`%**

```{r setup, include=FALSE}
# This globally prevents R code from appearing in the final document
knitr::opts_chunk$set(echo = FALSE)
```
##### Table key:
* input_size - number of features after pre-filtering based on max. % missing allowed in pools and samples
* missing_prefilter - number of features removed by pre-filtering based on max. % missing allowed in pools and samples
* filtered_by_rt -  number of features removed based on retention time if RT range is specified
* filtered_as_duplicates - number of duplicate features removed based on narrow M/Z and RT windows
* filtered_by_missingness - number of features removed from pre-filtered input based on % missing
* final_count - number of features in the dataset to be used for alignmnent

```{r}
kable(params$input_stats, caption = "Input data filtering results barchart")
```

```{r echo=FALSE, , fig.width=7, fig.height=5, fig.align='center', fig.cap="Data filtering barchart."}
params$filter_plot
```

```{r echo=FALSE, , fig.width=7, fig.height=5, fig.align='center', fig.cap="Batch-to-batch # of aligned features map."}
params$alignment_heatmap
```

```{r echo=FALSE, , fig.width=7, fig.height=5, fig.align='center', fig.cap="Adduct reproducibility in aligned data set"}
params$adduct_plot
```

```{r echo=FALSE, , fig.width=7, fig.height=5, fig.align='center', fig.cap="Aligned vs unaligned features in each batch based on UNFILTERED data sets."}
params$percent_aligned_plot
```

```{r echo=FALSE, , fig.width=7, fig.height=5, fig.align='center', fig.cap="Aligned vs unaligned features in each batch based on FILTERED data sets."}
params$percent_aligned_filtered_plot
```